comgen-outline

### 2017-12-16 paper/case2-habituals.Rmd
tweak habituals figs

rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
  filter(Parameter == "mean") %>%
  group_by(Variable, Gender, item) %>%
  summarize(MAP = estimate_mode(value),
            cred_upper = hdi_upper(value),
            cred_lower = hdi_lower(value)) %>%
  ungroup()
rs.habituals.bda.prior.summary.wide <- left_join(
  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
    select(-Variable) %>%
    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
    select(-Variable) %>%
    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
)

figure.habituals.priors.scatter <- left_join(rs.habituals.bda.prior.summary.wide,
          d.hab.priors %>% select(item, category)) %>%
ggplot(.,
       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
             fill = category))+
    scale_shape_manual(values=c(21,22))+
  #scale_color_solarized()+scale_fill_solarized()+
  scale_fill_brewer(palette='Set1')+

@@

example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
                       "goes to the movies_month", "smokes cigarettes_month")
fig.habituals.endorsement.vs.freq <- 
  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_jitter(width = 0.1, shape = 21, size = 5)+
  ylab("Human endorsement probability")+
  xlab("Frequency of target")+
  geom_label_repel(data = d.hab.endorsement.bayes %>% 
                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
                    filter(sentence %in% example.habituals), aes( label = habitual ),
                       color = 'black', fill = 'white',
    box.padding = unit(0.35, "lines"),
    point.padding = unit(1e-06, "lines"),
    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
  scale_x_continuous(limits = c(-1,6), 
                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 5))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "bottom")+
  coord_fixed(ratio = 7)+
  guides(fill = guide_colorbar(title = 'log annual rate',
                               ticks = F))
```
```{r habituals-items-table}
d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()

d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
  kable(.) %>% #, format = "latex", longtable = T, booktabs = T, caption = "a caption") %>% 
  #column_spec(3, width = "10cm")%>%
  collapse_rows(columns = 1:2)
```

@@

habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Speaker model - past frequency",
                                 "Speaker model - predictive frequency"

                                 ))) %>%
  filter(src == "Speaker model - past frequency") %>%
  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21, size = 4)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 1)+
  guides(fill = F)+
  #theme(legend.position = "bottom")+
  scale_fill_solarized()

habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Speaker model - past frequency",
                                 "Speaker model - predictive frequency"

                                 ))) %>%
  filter(src == "Speaker model - predictive frequency") %>%
  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21, size = 4)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 1)+
  #guides(fill = F)+
  #theme(legend.position = "bottom")+
  scale_fill_solarized()
#habituals.predictive.predictive.model
```

@@

left_join(m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Speaker model - past frequency",
                                 "Speaker model - predictive frequency"

                                 ))) %>%
  filter(src == "Speaker model - predictive frequency"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
```

```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline). Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation. Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 10, fig.height = 9.5, cache=F}
legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))

@@

grid.arrange(
  arrangeGrob(
    fig.hab.freq.predictive.vs.past, 
    fig.hab.endorse.vs.predfreq, 
    habituals.predictive.past.model, 
    habituals.predictive.predictive.model + theme(legend.position="none"),
    nrow=2, layout_matrix = cbind(c(1,3), c(2,4))),
legend_b, nrow=2,heights=c(8, 1))

#prow <- plot_grid(fig.hab.freq.predictive.vs.past, fig.hab.endorse.vs.predfreq, habituals.predictive.past.model, habituals.predictive.predictive.model #+ theme(legend.position="none"), labels = c("A", "B", "C", "D"), ncol = 2, align = 'v')

#plot_grid( prow, legend_b, ncol = 1, rel_heights = c(5, 0))
```

>>>>

rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
  filter(Parameter == "mean") %>%
  group_by(Variable, Gender, item) %>%
  summarize(MAP = estimate_mode(value),
            cred_upper = hdi_upper(value),
            cred_lower = hdi_lower(value)) %>%
  ungroup()
rs.habituals.bda.prior.summary.wide <- left_join(
  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
    select(-Variable) %>%
    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
    select(-Variable) %>%
    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
)
rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
          d.hab.priors %>% select(item, category)) 
figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide,
       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
             fill = category))+
    scale_shape_manual(values=c(21,22))+
  #scale_color_solarized()+scale_fill_solarized()+
  scale_fill_brewer(palette='Set1')+

@@

example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
                       "goes to the movies_month", "smokes cigarettes_month")
fig.habituals.endorsement.vs.freq <- 
  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_jitter(width = 0.1, shape = 21, size = 5)+
  ylab("Human endorsement probability")+
  xlab("Frequency of target")+
  geom_label_repel(data = d.hab.endorsement.bayes %>% 
                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
                    filter(sentence %in% example.habituals), aes( label = habitual ),
                       color = 'black', fill = 'white',
    box.padding = unit(0.35, "lines"),
    point.padding = unit(1e-06, "lines"),
    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
  scale_x_continuous(limits = c(-1,6), 
                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 5))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "bottom")+
  coord_fixed(ratio = 7)+
  guides(fill = guide_colorbar(title = 'log annual rate',
                               ticks = F))
```

```{r habituals-items-table, eval = F}
d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()

d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
  kable(., 
        format = "latex", longtable = T, booktabs = T,
        caption = "Demo table") %>% 
  kable_styling(latex_options = c("repeat_header"),
                font_size = 7)#%>%#, "hold_position")) %>%
  #column_spec(3, width = "10cm")%>%
  #collapse_rows(columns = 1:2)
```

@@

habituals.predictive.past.model <- m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Past-frequency endorsement model",
                                 "Predictive-frequency endorsement model"

                                 ))) %>%
  filter(src == "Past-frequency endorsement model") %>%
  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21, size = 4)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 1)+
  guides(fill = F)+
  #theme(legend.position = "bottom")+
  scale_fill_solarized()

habituals.predictive.predictive.model <- m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Past-frequency endorsement model",
                                 "Predictive-frequency endorsement model"

                                 ))) %>%
  #filter(src == "Predictive-frequency endorsement model") %>%
  ggplot(., aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = condition))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(shape = 21, size = 4)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("\n Model prediction")+
  ylab("Human habitual endorsement")+
  facet_wrap(~src, nrow = 1)+
  #guides(fill = F)+
  #theme(legend.position = "bottom")+
  scale_fill_solarized()
#habituals.predictive.predictive.model
```

@@

left_join(m.hab.predictive.endorse.rsa %>%
  mutate(src = factor(src, levels = c( 
                                      "past_model",
                                      "predictive_model"
                                     ),
                      labels = c(
                                 "Endorsement model (past frequency)",
                                 "Endorsement model (predictive frequency)"

                                 ))) %>%
  filter(src == "Endorsement model (predictive frequency)"), m.hab.predfreq.summary %>% rename(item = B, condition = D, freqmean = mean)) %>% View()
```

```{r habituals-predictive-figure, fig.cap="Top left: Predicted frequency of event (log-scale) as a function of (log) past frequency and condition manipulation (enabling, preventative, and baseline). Top right: Human endorsement of habitual sentences as a function of log predicted frequency and condition manipulation. Bottom row: Endorsement models based on past frequency (left) and measured predictive frequency (row).", fig.width = 13, fig.height = 3.5, cache=F}
legend_b <- get_legend(habituals.predictive.predictive.model + theme(legend.position="bottom"))

@@

plot_grid(
  fig.hab.freq.predictive.vs.past + 
    theme(plot.margin = unit(c(6,3,6,6), "pt")),
fig.hab.endorse.vs.predfreq + 
  theme(plot.margin = unit(c(6,0,6,6), "pt")),
# habituals.predictive.past.model + 
#   theme(plot.margin = unit(c(6,0,6,0), "pt")) + ylab(""),
habituals.predictive.predictive.model + 
  theme(plot.margin = unit(c(0,0,6,0), "pt")) + 
  theme(legend.position="none") + ylab(""),
align = 'h', 
labels = c("A","B","C"),
hjust = -1, nrow =1 , rel_widths = c(1.2, 0.95, 1.6))
```
